scRNAseq benchmark in want of a title

### 2019-06-18 bmc_article.tex

In addition to these methods, we reasoned that an approach such as DoubletFinder could be considerably sped up by being applied directly on counts and by using a pre-clustering to create neotypic doublets more efficiently. We therefore developed a simple and fast package implementing this for doublet detection, with the added advantage of accounting for uncertainty in the expected doublet rate and using meta-cells from the clusters to even include triplets (see methods).

>>>>

In addition to these methods, we reasoned that an approach such as DoubletFinder could be considerably sped up by being applied directly on counts and by using a pre-clustering to create neotypic doublets (i.e. doublets from different cell types) more efficiently. We therefore developed a simple and fast package implementing this for doublet detection, with the added advantage of accounting for uncertainty in the expected doublet rate and using meta-cells from the clusters to even include triplets (see methods).
